Analysis of Information Security Job Advertisements

### 2020-05-09 paper/paper.tex
Finish evaluation section.

\usepackage{graphicx}

@@

@@

With this setback, we now had to find another way to scrape this data. After taking a second look at the \textit{ScrapingBot} homepage, we saw that it is using headless \textit{Chrome} for its backend. We ventured further into this direction and found \textit{Selenium}, which can be used to programmatically use a web browser.

\textit{Selenium} supports all of the major web browsers, the only thing you need it the so called “webdriver” for the corresponding browser. Additionally, \textit{Selenium} can be used with a wide array of programming languages.

>>>>

\usepackage{graphicx}
\usepackage{listings}
\usepackage{hyperref}

@@

\newpage

@@

With this setback, we now had to find another way to scrape this data. After taking a second look at the \textit{ScrapingBot} homepage, we saw that it is using headless \textit{Chrome} for its backend. We decided to venture further into this direction and found \textit{Selenium}, which can be used to programmatically use a web browser.

\textit{Selenium} supports all of the major web browsers, the only thing you need is the so called “webdriver” for the corresponding browser. Additionally, \textit{Selenium} can be used with a wide array of programming languages. For our purposes we chose to go with the Ruby version of \textit{Selenium}. Specifically, we chose to use \textit{Rake}, which is similar to \textit{Make}, since it allows us to use the full functionality of \textit{Ruby} and specify tasks for each website. These scraping tasks can then be run with a simple \texttt{rake} command.

Given the setback we encountered on \texttt{monster.at}, the first thing we tried with \textit{Selenium} was to implement a simple task to extract the contents of the nested \texttt{iframe} element in their detail page layout. The first thing we needed to do was to fetch a job page. Next up, we needed to locate the nested \texttt{iframe} element; luckily this element is marked by a unique \texttt{id} field called \texttt{JobPreviewSandbox}. Once we had saved the nested \texttt{iframe} into a variable, we could use the \texttt{switch\_to} function provided by \textit{Selenium} to change to it from the main frame.

\begin{lstlisting}[language=Ruby]
iframe = find_element(id: 'JobPreviewSandbox')
switch_to.frame(iframe)
\end{lstlisting}

Seeing this proof-of-concept task working, we finally settled on using \textit{Selenium} and \textit{Rake} together with the \textit{Firefox} web browser.

As already briefly mentioned in \autoref{sub:evaluation_of_scraping_tools}, our goal was to implement scraping for Monster (\href{https://www.monster.at/}{\texttt{monster.at}}), Indeed (\href{https://at.indeed.com/}{\texttt{at.indeed.com}}) and StepStone (\href{https://www.stepstone.at/}{\texttt{stepstone.at}}). In this section we will go into more detail about the exact steps which were necessary to reliably scrape each respective website.

\subsubsection{Monster}
\label{subsub:monster}

\subsubsection{Indeed}
\label{subsub:indeed}

\subsubsection{StepStone}
\label{subsub:stepstone}
